---
title: "feature_symmetry_analysis"
author: "Maisy Hallam"
date: "2023-02-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = here::here())
library(tidyverse)

```

## R Markdown

First, we import all the dataframes - three for the simulations, three for the
kinbank data.

```{r read dataframes}
# sim_gender_data <- read_csv('data/frankenlanguages_gender.csv')
# sim_age_data <- read_csv('data/frankenlanguages_age.csv')
sim_lineage_data <- read_csv('data/frankenlanguages_lineage.csv')

# real_gender_data <- read_csv('data/kinbank_gender.csv')
# real_age_data <- read_csv('data/kinbank_age.csv')
real_lineage_data <- read_csv('data/kinbank_lineage.csv')


```

Delete NA rows from the data, and remove any extra headings.

```{r clean up the data}
# sim_gender_data <- sim_gender_data[!(sim_gender_data$GENDER=='GENDER'),]
# 
# sim_age_data <- sim_age_data[!(sim_age_data$AGE=='AGE'),]
# 
sim_lineage_data <- sim_lineage_data[!(sim_lineage_data$LINEAGE=='LINEAGE'),]

sim_lineage_data <- sim_lineage_data[!apply(is.na(sim_lineage_data_new) | sim_lineage_data_new == "", 1, all),]

```

Mutate the dataframes to include a column specifying whether the data was simulated
or if it's from kinbank.

```{r mutate the data}

# sim_gender_data <- sim_gender_data %>%
#   mutate(
#     TYPE = 'simulated'
#   )

# sim_age_data <- sim_age_data %>%
#   mutate(
#     TYPE = 'simulated'
#   )
# 
sim_lineage_data %>%
  mutate(
    TYPE = 'simulated'
  )

# real_gender_data <- real_gender_data %>%
#   mutate(
#     TYPE = 'kinbank'
#   )

# real_age_data <- real_age_data %>%
#   mutate(
#     TYPE = 'kinbank'
#   )
# 
real_lineage_data %>%
  mutate(
    TYPE = 'kinbank'
  )

```

Merge the two data frames for each feature.

```{r merge the dataframes}
# gender_data <- rbind(sim_gender_data, real_gender_data)
# age_data <- rbind(sim_age_data,real_age_data)
lineage_data <- rbind(sim_lineage_data,real_lineage_data)

```

Plot the gender data proportions to compare simulated and kinbank languages.

```{r bar plot gender data}
gender_data %>%
  ggplot(aes(x=GENDER, fill=TYPE)) +
  geom_bar(aes(y=..count../tapply(..count.., ..fill.. ,sum)[..fill..]), position='dodge')


```


```{r}
age_data %>%
  ggplot(aes(x=AGE, fill=TYPE)) +
  geom_bar(aes(y=..count../tapply(..count.., ..fill.. ,sum)[..fill..]), position='dodge')
```

```{r}
lineage_data %>%
  ggplot(aes(x=LINEAGE, fill=TYPE)) +
  geom_bar(aes(y=..count../tapply(..count.., ..fill.. ,sum)[..fill..]), position='dodge')
```



