---
title: "What's wrong with my sims :("
author: "Maisy Hallam"
date: "2023-03-31"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse) # for data preprocessing
library(ggplot2) # for plotting
library(lme4) # for model fitting
```

# Preprocessing the data

## Import the data

First, we import all the raw data.

```{r import}
gender_prop_files <- list.files(path="data/gender/prop/",pattern="*.csv",full.names=TRUE)
gender_data <- do.call(rbind, lapply(gender_prop_files, function(x) read.csv(x)))
```

## Process the data

We add a column TYPE which tells us if the data comes from kinbank or if it is simulated, and we delete the first two columns because I am an idiot who ran my include_headings function too many times.

```{r}
gender_data <- gender_data %>%
  mutate(
    
    TYPE = ifelse (grepl('frankenlanguage', LANGUAGE),
    'simulation',
    'kinbank'
  ))

gender_data <- gender_data[-2,]
```

And then we save gender_data to a new CSV file.

```{r}
write.csv(gender_data, 'data/processed/all_gender_proportions.csv')
```

Now, let's split `gender_data` into two dataframes - `kinbank` and `simulations`.

```{r}
kinbank <- filter(gender_data,TYPE == 'simulation')
simulations <- filter(gender_data,TYPE == 'kinbank')
```

And save those too.

```{r}
write.csv(kinbank, 'data/processed/kinbank_gender_proportions.csv')
write.csv(simulations, 'data/processed/simulated_gender_proportions.csv')

```

# Analysis

We need the means of each SET of data - so all 1000 simulations, plus the kinbank data.

```{r}
simulations %>% group_by(SET)
```


```{r}
kinbank %>%
  ggplot() +
  geom_bar(aes(x=GEN_0,y=count,fill=sample)
```


